Transforming Trash as an Artistic Act

### 2015-11-22 chapter1.tex
reorganization.
Former-commit-id: 62458277abba8bfebb14b71b84540e80d4c45502

\comment{not shared thing, perception of waste is not static.} \paraphrase{"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others. The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions. Worthless. Rejected and useless matter of any kind. Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream. Our trash is part of us, whether or not we choose to acknowledge it." \cite{zimring2012encyclopedia}}

In this thesis work to understand the different aspects of trash is a key element. Because as scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here). Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed. On the other hand it is accepted as a source of diversity. (To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)). Therefore we should ask these questions: What is trash? How does it became trash? Is it a end product or a source material? How much is it valuable? How much is it dangerous?

In previous ages (which age? pre industrial ages?) objects and resources are used again and again. Production of objects are hard and laborious. \comment{Böyle çok fazla kullanılan nesneye örnek bulsak ne kadar güzel olur. Mendillere bunlara örnek olabilir. Aslında tam benim konumla ilgili çünkü tek kullanımlık. Hijyen kavramıyla ilgili giderek artan da bir ilgi necesiyle tek kullanımlık peçeteler gittikçe önem kazanıyor.} \todo{Susan Strasser}

% Trash is everywhere and, produced every time
Modern (developed) societies are continuously generating trash and, pile them on landfills. It's a common object category that all people share its possession (It is experienced by everybody.). During daily activities trash is generated and people get rid of them by throwing away. (Various objects become trash after their primary functions daily. Who defined the primary function? Primary function is the only function. People do not care the package of the objects that they buy. They buy the coffee not the cup of it. After coffee finished the life of cup also finishes. There is a lifetime defined (or forecast) by the producer of objects. However it is not bound to the producer, also consumer play an important role. There are different choices. Throw it away. Keep it. Give it. Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. They are not easily disposable items. They live in the nature thousands of years. They are durable(in terms of resistant to natural affects) products. Most of them packages that are used to carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.)

@@

% Introduction of ReVista
\quotes{As I prepared this issue of ReVista, some have asked me if Bogotá’s garbage crisis inspired the theme. Yes and no. After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast. Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects. No one called it recycling. Trash was to be used and used again.}\cite{} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash. They can not handle their trash. There is no place for trash in their life.

% FROM Trash as Treasure, BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
% TODO PRAP. REF.
\todo{Facts about trash} \paraphrase{Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever. The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.}

% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
% TODO PRAP. REF.
\paraphrase{We relate to garbage daily. We use it, produce it and dispose of it. Endlessly. The most obsessive of us get rid of it as fast as we can. The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes. We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations). Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding. Particularly in the connection between garbage and the arts, I am interested in two questions. First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.}

People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore. However is it really values? What does make it valueless? They do not think what happens after they throw it away. It exits from your life but not the world. What happens when you throw away a It is stacked from another place. Value of objects are not static. Trash is not static also It has a long journey. A project conducted by MIT researches journey of trash by placing trackers onto the trash. The results are surprising. Trashes spread away across the country and this journey takes month. \todo{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo{footnote what are these countries?}. In other worlds Americans trash is not only their trash. As commodities spread to the every corner of the world, trash also. What happens when it is traveled to the other countries, how they approaches these items. \comment{They find new uses and meanings on them.} \todo{consider Papua genen people}

% Cycle of trash
Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to land fills. From garbage baskets to sculptures. [REF. MIT Garbage project] Lots of different people touches to trash. With the trash what moves?

Even if people pay little attention, everybody do not. An artist takes photos of his every trash, like people take photos of their faces. He focuses on the thing that paid little attention, that is trash. At the end he exhibits all the photos by covering all the walls of room. It can seen as record of his activities, record of commodities. Most of them we are not aware of them. Draw the attention of is being thrown away and everytime and everywhere. They are too much and can only fit covering all the walls. \todo{artist}

% ARTWORK
% Sad chair http://www.keaggy.com/chairs/sad/12/. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.

@@

\todo{Background information about the thesis. Inspirational points. facts of trash\ldots}

@@

\todo{ArtBin, trashing things?}

%****************************************
% Different types of trash
\todo{Different types of trash.} \comment{There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.}

@@

%****************************************
% Different disciplines, Perspectives related with trash from different disciplines
\todo{List of disciplines, and their approach to the trash.} \comment{Trash draws attention different peoples and disciplines. In other words there are different studies related with trash. Different approaches to the trash and son on.}

@@

This is very important because the problem of trash is being tried to be handled by different disciplines. In other words there different approaches to the trash. Different problems, different solutions. Which perspective that I have. In what ways my project differs from them. The purpose is to participate people in this work, by collecting them etc. And also offer to transform it. Rescue it and than later transform it. In short, the difference between the other disciplines must be clear. 
\begin{itemize}
\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
\item Management of it (handled by the municipals generally).
\item Technological perspectives. (seeing trash as a design problem. developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed? development in what sense?)
\end{itemize}
%........................................

%%%
%%%
%%%
\section{Purpose of the Study}
\todo{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}

@@

\comment{How does it become trash?} Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

%%%
%%%
%%% 
\section{Overview of Chapters}
This study is structured many examples of artworks in different part of the thesis. As the related topic or argument is presented example artwork is given at this moment. Immediately how artist replies this issue is illustrated. Thereby artworks are examined in the theoretical and cultural context. Art works are used as a supportive elements for the stated arguments. \comment{yeri geldikçe de gene bu işlere ele alınmış farklı açılardan incelenmiştir.} \comment{Sanat eserlerinin tümüyle bir çözümlemesi her yerde yapılamamıştır, konuyla ilgili kısımlarına değinilmiştir.}

Following chapter ---Trash in Culture and Theory--- explores the place of trash in the cultural life and theoretical approaches on trash. The aim is (better) to understand the trash in cultural and theoretical aspects. (to better realization the notion of trash.) It is explored the trash is being worked is whose trash. Or what type of society genarete this trash. Also in the project I collect the paper trash. What type of approach generate it and what are the dynamics of it? What type of trash we are talking about? It is understood through the patters of consumption patterns. And to reflect this cultural phenomena what phylosphers and scholars say. Artist how they are reflected this notion.and also looked how scholars are conceptualized trash and its movement on the different values system. How explained the transient nature of trash?

\comment{First chapter will be about the conceptual framework that I have been working through which includes historical and theoretical background.}

Third chapter seeks the root of using trash in the artworks and looks through the sample artworks. As already artworks are mentioned in the different part of the thesis, in this chapter focused on art (historical )

Fourth chapter explains the project that supports this thesis. Its stages and approaches to the topic mentioned here.

\comment{The second chapter will consist of the overview of my work. I will start with the development process of the work. I believe that the way an artist works and the obstacles that she encounters have a huge impact on how the final work is embodied. Development process of my work shaped the way I think on the subject of my thesis. Therefore, I will explain my process as detailed as possible. Then, I will continue with different aspects of my work; formal decisions and usage of light that I believe carry my work to another level. At the end of this chapter, we will see how my work functions and what it proposes on the image and word relationship.}

Finally last chapter offers an overall conclusion of this thesis and project.

\comment{The final section, procedural description, covers the process of the project from beginning to end. The final chapter is reserved for conclusion. The overall project is summed up and the significance and the purpose of the project is re-emphasized.}

%%%
%%%
%%%
\section{A Note on Terminology}
(Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash. Although there are slight differences between these words, sometimes they are used to signify same concept (or used with same purposes). It is important to understand diverse vocabulary of this topic before dive into the theory. It is very important to choose right terminology, because ... and also make more clearer the borders of the work. There is no agreed (or specific) terminology. Some scholars uses junk art, others recycling art. Sometimes this make difficult to research on this topic. And also I must point out that this topic is not limited with the English language. The topic is broad and it is not limited with English literature and vocabulary (ref required).

% FROM Rubbish! The Archaeology of Garbage, p.9
Several words for the things we throw away---"garbage", "trash", "refuse", "rubbish"--- are used synonymously in causal speech but in fact have different meanings. \textit{Trash} refers specifically to discards that are at least theoretically "dry"---newspapers, boxes, cans, and so on. \textit{Garbage} refers technically to wet discards--- food remains, yard waste, and offal. Refuse is an inclusive term for both the wet discards and the dry. Rubbish is even more inclusive: It refers to all refuse plus construction and demolition debris. The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrevelant, but may see a revival if the idea of composting food and yard waste catches on. We will frequently use "garbage" in this book to refer to the totality of human discards because it is the word used naturally in ordinary speech. The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen.

The origin of vocabulary of this topic reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?

@@

According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form. If any item is used again and again over time, it is said to be reused. The main purpose of reusing is to lengthen the life of the item or material. Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others. The main purpose is to make the item last as long as it can. To reuse is to use something again instead of throwing it away or sending it off to a recycling company. Why throw something away when you can give it another life? Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product. Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose. For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.

@@

\paraphrase{Not all artist transform trash although some deconstruct them. Michael Landy is one of them. Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers. Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part. Reveal all his possessions. and loosing them while you are alive. Turning them to rubbish making them unusable. breaking down the all the meaning. breaking down the connections.} It can be an example of downcycling process. It is prefered to decompse all the complex link and relationships between the objects. They are not just ordinary things they are possessions of artist. Break Down 2001, in which he systematically destroyed all his personal possessions. His work examines what we value and what we discard, consumerism and waste, and human labour and its worth. It happens in public space. People can see the process. This process last 2 weeks. Places where people buy things actually.

@@

>>>>

Common perception to the trash is to get rid of it as soon as possible. People want to depose trash from their lives most of time not thinking beyond. However to establish solid understanding of trash, we have to give attention to the trash and ask why it is trash? How does it become trash?

\paraphrase{"Every day, we put unwanted material in toilets and garbage bins, regularly flushing it away or taking it out in bags to be transported far away from our homes by others. The names we give this material---waste, garbage, refuse, trash, rubbish--- have pejorative definitions. Worthless. Rejected and useless matter of any kind. Unimportant." "Our trash is a testament; what we throw away says much about our values, our habits, and our lives." "While dictionary definitions of garbage describe it as “filth” and “worthless,” scholars are careful to note that perceptions of waste and the value of material are neither static nor universally shared." "\ldots the question of who owns these discards is not trivial." "The absence of a waste stream aroused suspicion, just as the presence of particular items tell us about the habits of the consumers who generate a waste stream. Our trash is part of us, whether or not we choose to acknowledge it. \todo{ref for tracey emin et al.}" \cite{zimring2012encyclopedia}}

In this thesis work to understand the different aspects of trash is a key element. \todo[inline]{This aspects are \ldots} As scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed cities to rural areas, from modern societies to ancient societies. Sometimes it is accepted as a problem (waste crises, ecological problems.) that is need to carefully and seriously managed. On the other hand it is accepted as a source of diversity. (To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?) or aspects). Therefore we should ask these questions: What is trash? How does it became trash? Is it a end product or a source material? How much is it valuable? How much is it dangerous?

%\comment{In previous ages (which age? pre industrial ages?) objects and resources are used again and again. Production of objects are hard and laborious. Böyle çok fazla kullanılan nesneye örnek bulsak ne kadar güzel olur. Mendillere bunlara örnek olabilir. Aslında tam benim konumla ilgili çünkü tek kullanımlık. Hijyen kavramıyla ilgili giderek artan da bir ilgi necesiyle tek kullanımlık peçeteler gittikçe önem kazanıyor. Peki burda illaha geçmişe falan girmek gerek var mı? çok mu derdimde benim?}

%\comment{Dört bir yanımız metalarla çevrilmş durumda, istediğimiz şeylere çok kolay bir şekilde ulaşabiliyoruz. Yemek siparişi veriyoruz ayağımıza geliyor. İki blok ötedeki kahveciden istediğimiz zaman kahvemizi alıyoruz. Ama tüm bunların bir bedeli var. Bir yandan da sürekli olarak çöp üretiyoruz. Her ne kadar son derece sistemli bir şekilde çöpler toplanıyor ve belki de ne kadar tüketildiğini hiçbir zaman farkına var mıyoruz?}

% Trash is everywhere and, produced every time
Modern (developed) societies are continuously generating trash and, pile them on landfills. It is experienced by everybody, part of the production of garbage. During daily activities trash is generated and people get rid of them by throwing away as quickly as possible. (Various objects become trash after their primary functions consumed. People do not care the package of the objects that they buy. They buy the coffee not the cup of it. After coffee finished the life of cup also finishes. Very small life. But is that really so? Is that really life of an object ends after tossed on the waste bin? \todo[inline]{No. Rubbish theory says opposite of it.} (some of the garbage live more from us. we use it 5minutes it will still exist years.) There is a lifetime defined (or forecast) by the producer of objects. However it is not bound to the producer, also consumer play an important role. There are different choices. Throw it away. Keep it. Give it. Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. They are not easily disposable items. They live in the nature thousands of years. They are durable(in terms of resistant to natural affects) products. Most of them packages that are used to carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.)

@@

% Introduction of ReVista
\paraphrase{After Christmas, I traveled with a group of friends to the Chocó, an isolated and impoverished region on Colombia’s Pacific Coast. Christmas decorations abounded, and I noticed they were almost all crafted from used tin cans, old newspapers, discarded textiles and found wood objects. No one called it recycling. Trash was to be used and used again.} Already a group of people live with their trash, what is problematic is here global ruling consumerist is not live with their trash. They can not handle their trash. There is no place for trash in their life. 
\todo[inline]{herkes için bu geçerli değil yani o zaman ilk baştaki yere referans veriyoruz.}

% FROM Trash as Treasure, BY WILLIAM L. FASH AND E. WYLLYS ANDREWS, ReVista
% TODO PRAP. REF.
\todo[inline]{Facts about trash} \paraphrase{Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever. \textbf{The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization.} The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment.}

% From Beautiful Trash Art and Transformation BY PAOLA IBARRA, ReVista
% TODO PRAP. REF.
\paraphrase{\textbf{We relate to garbage daily. We use it, produce it and dispose of it. Endlessly. The most obsessive of us get rid of it as fast as we can.} The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes. We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations). Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding. Particularly in the connection between garbage and the arts, I am interested in two questions. First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material.}

People tend to think that trash is valueless because it is trashed no longer needed or not wanted anymore. However is it really values? What does make it valueless? They do not think what happens after they throw it away. It exits from your life but not the world. What happens when you throw it away? It is stacked from another place. Value of objects are not static. Trash is not static \todo[inline]{ilk paragrafa referans} also it has a long journey. A project conducted by MIT researches journey of trash by placing trackers onto the trash \cite{chen2009mit}. The results are surprising. Trashes spread away across the country and this journey takes month. \todo[inline]{give exact reference} We know that it is not limited with the border of America because it is the one of the countries export their garbage to the other countries --- fourth world countries\todo[inline]{footnote what are these countries?}. In other worlds Americans trash is not only their trash. As commodities spread to the every corner of the world, trash also. What happens when it is traveled to the other countries, how they approaches these items. \comment{They find new uses and meanings on them.} \todo[inline]{consider Papua genen people}

\begin{quote}
\paraphrase{“Nobody wonders where, each day, they carry their load of refuse. Outside the city, surely; but each year the city expands, and the street cleaners have to fall farther back. The bulk of the outflow increases and the piles rise higher, become stratified, extend over a wider perimeter” – Italo Calvino, Invisible Cities} The project is an initial investigation into understanding the 'removal-chain' in urban areas and it represents a type of change that is taking place in cities: a bottom-up approach to managing resources and promoting behavioral change through pervasive technologies. TrashTrack builds on previous work of the SENSEable City Lab in its exploration of how the increasing deployment of sensors and mobile technologies radically transforms how we understand and describe cities. “People just take their trash and put it on the curb and they forget about it and don’t think about all the time and energy and money put into disposing of it.”
\end{quote}

% Cycle of trash
Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to land fills. From garbage baskets to sculptures. \todo[inline]{REF. MIT Garbage project} Lots of different people touches to trash. With the trash what moves?

%http://timgaudreau.com/2012/trash/trash.html
\comment{Self-Portrait as Revealed by Trash} Even if people pay little attention, everybody do not. An artist takes photos of his every trash, like people take photos of their faces. He focuses on the thing that paid little attention, that is trash. At the end he exhibits all the photos by covering all the walls of room. It can seen as record of his activities, record of commodities. Most of them we are not aware of them. Draw the attention of is being thrown away and every time and everywhere. They are too much and can only fit covering all the walls. \todo[inline]{Tim Gaudreau “Self-Portrait as Revealed by Trash: 365 days of photographing everything I threw out – Variation I, 2006”} \paraphrase{After photographing my trash over the course of the year, I ended up with 5,000 images representing my waste stream. These collections of grids represent my first experiments with using those images. This initial work ultimately led to the full scale collages that have become my Self-portrait as Revealed by Trash: 365 days of photographing everything I threw out.}

% ARTWORK http://www.keaggy.com/chairs/sad/12/
\todo[inline]{Sad chair. Photos of lonely chairs that are no longer wanted. Artist captures the continuously left alone chairs.}

@@

@@

\todo[inline]{ArtBin, trashing things?, squuezzing, wall-e}

%http://www.smithsonianmag.com/arts-culture/photographer-creates-fine-art-out-trash-we-throw-environment-180951615/?no-ist
\todo[inline]{showing them as they are, Barry Rosenthal}

%****************************************
% Different types of trash
\todo[inline]{Different types of trash.} \comment{There are many works from trash around the world. Build up trash. Collected from graveyards, landfills, unused materials etc.}

@@

%****************************************
% Different disciplines, Perspectives related with trash from different disciplines
\todo[inline]{List of disciplines, and their approach to the trash.} \comment{Trash draws attention different peoples and disciplines. In other words there are different studies related with trash. Different approaches to the trash and son on.}

@@

This is very important because the problem of trash is being tried to be handled by different disciplines. In other words there different approaches to the trash. Different problems, different solutions. Which perspective that I have. In what ways my project differs from them. The purpose is to participate people in this work, by collecting them etc. And also offer to transform it. Rescue it and than later transform it. In short, the difference between the other disciplines must be clear. 
\begin{itemize}
\item Ecological perspective: Trash causes ecological problems and it treats the balance of nature. Animals do not aware of plastics materials and they unconsciously eat them.
\item Management of it (handled by the municipals generally).
\item Technological perspectives. (seeing trash as a design problem. developed technologies and societies generates lots of trash, so this situation cause to inquiry that are they really developed? development in what sense?)
\end{itemize}

\comment{Trash draws attention of many scholars and people who are professional in different areas. Further trash is a common subject of the all ages through the human history. In other words this topic is not introduced in recent years (or ages). It always part of the human practice and life. Even if trash is refused and discarded thing, there are people giving attention to them.}
%........................................

%%%
%%%
%%%
\section{Purpose of the Study}
\todo[inline]{what do you mean when saying ``transforming trash"? Needs to be opened. I claimed that such a thing exist? when it is exist? by physically or conceptually? actually both of them exist.}

@@

\comment{How does it become trash?} Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a road map (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

%%%
%%%
%%% 
\section{Structure of the Study}
This study is structured by many examples of artworks in different part of the thesis. When a topic or argument is presented, immediately example artwork is given at this moment and how artist replies this issue is illustrated. Thereby artworks are examined in the theoretical and cultural context. Artworks are used as a supportive elements for the stated arguments.  However, not every time artworks are discussed in detail. Only basic information is given and how it is related with this topic explained. \comment{By the way} it is better to keep in mind that all works can be analyzed in different contexts in more detail fashion.

Following chapter, Trash in Culture and Theory, explores the place of trash in the cultural life and theoretical approaches on trash. The aim is (better) to understand the trash in cultural and theoretical aspects. (to better realization the notion of trash.) Provides theoretical and cultural background. It is explored the trash is being worked is whose trash. Or what type of society generate this trash. Also in the project I collect the paper trash. What type of approach generate it and what are the dynamics of it? What type of trash we are talking about? It is understood through the patters of consumption patterns. And to reflect this cultural phenomena what philosophers and scholars say. Artist how they are reflected this notion.and also looked how scholars are conceptualized trash and its movement on the different values system. How explained the transient nature of trash?

Third chapter, Trash (in) Art, seeks the root of using discarded materials in the artworks and looks through the sample artworks and artists. As already artworks are mentioned in the different part of the thesis, in this chapter some of them analyzed deeply. Artists methods and approaches to the subject are stated.

\comment{Fourth chapter consists of the overview of the project. Stated the approach to topic clearly. Development process of the work is presented in detail. I will start with the development process of the work. I believe that the way an artist works and the obstacles that she encounters have a huge impact on how the final work is embodied. Development process of my work shaped the way I think on the subject of my thesis. Therefore, I will explain my process as detailed as possible. Then, I will continue with different aspects of my work; formal decisions and usage of light that I believe carry my work to another level. At the end of this chapter, we will see how my work functions and what it proposes on the image and word relationship.}

\comment{Finally last chapter is reserved for an overall conclusion of this thesis and further suggestions on the subject and the project.}

%%%
%%%
%%%
\section{A Note on Terminology}
Within the scope of thesis only words that are English is examined but in different languages and cultures there might be different naming for various stages of object and trash. Analysis of them may be subject of another thesis. (Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash. Although there are slight differences between these words, sometimes they are used to signify same concept (or used with same purposes). Understanding diverse vocabulary of this topic before dive into the theory makes more clearer the borders of the work. There is no consensus on terminology. Some scholars uses junk art, others recycling art. The origin of vocabulary of this topic reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined? From the rubbish: the archeology of garbage gives clearer definition of some these words.

% FROM Rubbish! The Archaeology of Garbage, p.9
Several words for the things we throw away---"garbage", "trash", "refuse", "rubbish"--- are used synonymously in causal speech but in fact have different meanings. \textit{Trash} refers specifically to discards that are at least theoretically "dry"---newspapers, boxes, cans, and so on. \textit{Garbage} refers technically to wet discards--- food remains, yard waste, and offal. Refuse is an inclusive term for both the wet discards and the dry. Rubbish is even more inclusive: It refers to all refuse plus construction and demolition debris. The distinction between wet and dry garbage was important in the days when cities slopped garbage to pigs, and needed to have the wet material separated from the dry; it eventually became irrelevant, but may see a revival if the idea of composting food and yard waste catches on. We will frequently use "garbage" in this book to refer to the totality of human discards because it is the word used naturally in ordinary speech. The word is etymologically obscure, though it probably derives from Anglo-French, and its earliest associations have to do with working in the kitchen.

Some notes on methods:

@@

According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form. Reusing lengthens the life of the item or material. Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others. The main purpose is to make the item last as long as it can. To reuse is to use something again instead of throwing it away or sending it off to a recycling company. \textbf{Why throw something away when you can give it another life?} Reusing is significant way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product. Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose. For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[height=6cm]{graphics/ChrisJordan_BreakDown.jpg}
  \caption{Chris Jordan, Break Down}
  \label{fig:ChrisJordan_BreakDown}
\end{figure}

\paraphrase{Not all artist transform trash although some deconstruct them. Michael Landy is one of them. Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers. Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part. Reveal all his possessions. and loosing them while you are alive. Turning them to rubbish making them unusable. breaking down the all the meaning. breaking down the connections.} It can be an example of downcycling process. It is preferred to decompose all the complex link and relationships between the objects. They are not just ordinary things they are possessions of artist. Break Down 2001, in which he systematically destroyed all his personal possessions. His work examines what we value and what we discard, consumerism and waste, and human labour and its worth. It happens in public space. People can see the process. This process last 2 weeks. Places where people buy things actually.

@@

In this thesis scope mainly \comment{tek kullanımlık} objects are considered generally. Nearly half of the material used in the project is disposable packets. Therefore as well as other words used but mainly trash is used to refer the material.

Some of the scholar uses recycling\cite{cerny1996recycled,herman1998trashformations} for the recreation and transformation of it. Some of the scholars and artist uses upcycling for their process.
